Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-27 eg6-letters/incoherent/incoherent_prl.tex
some more cleaning

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries and independent of $t$ for a bound proton compared to the 
free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated 
from the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the 
difference becomes large at lower $x_B$, where the off-shell model predicts an 
enhancement of the ratio, while our experiment shows no sign of an increase of 
ratios. This measurement shows that an important nuclear effect is missing from 
the existing models in order to explain this strong quenching of the BSA. More 
theoretical developments will be needed to identify the origin of this 
quenching, in particular it will be key to differenciate initial from final 
state effects and how they can affect the DVCS assymetries.

>>>>

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries and independent of $t$ for a bound proton compared to the 
free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated 
from the quark-meson coupling model \cite{Guzey:2008fe}. Our results show that 
an important nuclear effect is missing from the existing models in order to 
explain this strong quenching of the BSA.  More theoretical developments will 
be needed to identify the origin of this quenching, in particular it will be 
key to differenciate initial from final state effects and how they can affect 
the DVCS assymetries.
